A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-09-14 article/article.tex

\begin{itemize}
    \item There is a lot of knowledge in the literature on how to define archetypes of traffic scenes.
    \item Once an archetype is defined, a special property of graphs can be used. 
    \item Two graphs are isomorphic if they have the same structure, regardless of the node and edge labels.
    \item As the archetypes are not necessarily are involving a lot of actors, these are more like subsets of actual traffic scenes.
    \item A very simple example might be 2 vehicles on the same lane, driving in the same direction and another vehicle driving on a neighboring lane.
    \item This situation can be represented by a graph with 3 nodes and 2 edges. 
    \item In most real traffic situations however, there will be additional actors present, so that we are not searching for isomorphic graphs, but rather want to check if any subgraph of $G$ is isomorphic to the archetype graph $A$.
    \item This is an example of a subgraph isomorphism problem.
    \item While this problem is NP-hard, the graphs considered here are rather small, so the computational time is reasonable.
    \item One such algorithm is the VF2 algorithm, which is implemented in the NetworkX library. <- Check and cite something.
    \item The strategy we are then applying is 
\end{itemize}

@@

>>>>

\begin{itemize}
    \item There is a lot of knowledge in the literature on how to define archetypes of traffic scenes.
    \item Once an archetype is defined, a special property of graphs can be used. 
    \item Two graphs are isomorphic if they have the same structure, regardless of the node and edge labels.
    \item As the archetypes are not necessarily are involving a lot of actors, these are more like subsets of actual traffic scenes.
    \item A very simple example might be 2 vehicles on the same lane, driving in the same direction and another vehicle driving on a neighboring lane.
    \item This situation can be represented by a graph with 3 nodes and 2 edges. 
    \item In most real traffic situations however, there will be additional actors present, so that we are not searching for isomorphic graphs, but rather want to check if any subgraph of $G$ is isomorphic to the archetype graph $A$.
    \item This is an example of a subgraph isomorphism problem.
    \item While this problem is NP-hard, the graphs considered here are rather small, so the computational time is reasonable.
    \item One such algorithm is the VF2 algorithm, which is implemented in the NetworkX library. <- Check and cite something.
    \item The strategy we are then applying is a simple counting strategy.
    \item TODO: Create pseudo code for double loop counting strategy.
    \item This strategy can be described to some degree as a bottom up approach: Starting from a detail level, individual situations are defined.
    \item Then going upwards to different datasets, it is checked, if the archetype is present.
\end{itemize}

@@

\begin{itemize}
    \item One often utilized strategy in machine learning is to translate raw data like images or text into an embedding space in order to be  
\end{itemize}
